\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-27 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_10pg.tex
updates

@@

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of transient stochastic states for the IEEE 14 bus system for the nominal case as well as for the case when a line failure occurs. In Sec. \ref{subsec:NumSimSynthetic}, we propagate the joint PDFs over the 100 dimensional state space of a synthetic power network with randomly generated parameters--our intent there is to highlight the scalability of the proposed method.

All simulations were performed in MATLAB R2019b on an iMac with 3.4 GHz Quad-Core Intel Core i5 processor and 8 GB memory.

@@

Our numerical simulations for the IEEE 14 bus system consider the following three cases:

\noindent\textbf{Case I.} Nominal case where ...

\noindent\textbf{Case II.} post-contingency simulation after the line 13 fails.

\noindent\textbf{Case III.}	load data are time-varying ...

For all the three cases, we used the randomly generated noise coefficients $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

We take the initial joint PDF as
\begin{align}
\rho_{0}&\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \vartheta_{0}\left(\bm{\theta}(0)\right)\Omega_{0}\left(\bm{\omega}(0)\right)\nonumber\\
&=\underbrace{\left(\prod_{i=1}^{n=5}\dfrac{\exp\left(\kappa_{i}\cos\left(2\theta_{i}(0)-\mu_{\theta_{i}(0)}\right)\right)}{2\pi I_{0}(\kappa_{i})}\right)}_{=:\vartheta_{0}\left(\bm{\theta}(0)\right)}\nonumber\\
	&\qquad\times \underbrace{{\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right)}_{=:\Omega_{0}\left(\bm{\omega}(0)\right)},
\label{rho0IEEE14}		
\end{align}
whose $\bm{\theta}$ marginal $ \vartheta_{0}\left(\bm{\theta}(0)\right)$ is a product von Mises PDF\footnote{the factor $2$ inside the cosine ensures the range $[0,2\pi)$; it can be dispensed if we instead use the range $[-\pi,\pi)$ for the angular variables, as common in the directional statistics literature \cite{mardia2009directional}.} \cite{mardia2008multivariate,mardia2014some} supported over $\mathbb{T}^{5}$ with mean angles (in rad)
\begin{align}
\left(\mu_{\theta_{1}}(0),\hdots,\mu_{\theta_{5}}(0)\right)=\left(0, 6.1963, 6.0612, 6.0350, 6.0500\right),
\label{MeanAngleInitialIEEE14}	
\end{align}
and concentration parameter $\kappa_{i}\geq 0$ set as 
\[(\kappa_{1},\hdots,\kappa_5) = \left(5,6,7,4,5\right).\]
In \eqref{rho0IEEE14}, $I_{0}(\cdot)$ denotes the modified Bessel function of the first kind with order zero, given by $I_{0}(\kappa) = \sum_{r=0}^{\infty} \frac{\left(\kappa^{2}/4\right)^{r}}{(r!)^{2}}$, and can be evaluated via MATLAB command \texttt{besseli(0,$\cdot$)}.

>>>>

\begin{remark}\label{remark:timevaryingEffectivePowerInput}
The proposed computational framework can be applied as is when $P_{i}^{\rm{mech}}, P_{i}^{\rm{load}}$, and thus $P_{i}$ in \eqref{defPi}, are bounded time-varying functions. {\red{This can be the case, for instance, when ...}} 	
\end{remark}

@@

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of transient stochastic states for the IEEE 14 bus system for the nominal case as well as for the case when a line failure occurs. In Sec. \ref{subsec:NumSimSynthetic}, we propagate the joint PDFs over the 100 dimensional state space of a synthetic power network with randomly generated parameters--our intent there is to highlight the scalability of the proposed method. All simulations were performed in MATLAB R2019b on an iMac with 3.4 GHz Quad-Core Intel Core i5 processor and 8 GB memory.

@@

Our numerical simulations for the IEEE 14 bus system consider the following two cases:

\noindent\textbf{Case I.} {\red{Nominal case where ...}}

\noindent\textbf{Case II.} {\red{post-contingency simulation after the failure of line 13 (see Fig. \ref{fig:Motivating}).}}

%\noindent\textbf{Case III.}	load data are time-varying ...

For all the cases mentioned above, we used the randomly generated noise coefficients $\sigma_{i}\in [1,5]$ as
\[(\sigma_{1},\hdots,\sigma_5) = \left(2.4628, 4.9266, 4.8724, 1.4215, 3.8681\right).\]

To account the pertinent geometry of $\mathbb{T}^{n}\times\mathbb{R}^{n}$, we take the initial joint PDF as
\begin{align}
\rho_{0}&\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \vartheta_{0}\left(\bm{\theta}(0)\right)\Omega_{0}\left(\bm{\omega}(0)\right)\nonumber\\
&=\underbrace{\left(\prod_{i=1}^{n=5}\dfrac{\exp\left(\kappa_{i}\cos\left(2\theta_{i}(0)-\mu_{\theta_{i}(0)}\right)\right)}{2\pi I_{0}(\kappa_{i})}\right)}_{=:\vartheta_{0}\left(\bm{\theta}(0)\right)}\nonumber\\
	&\qquad\times \underbrace{{\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right)}_{=:\Omega_{0}\left(\bm{\omega}(0)\right)},
\label{rho0IEEE14}		
\end{align}
whose $\bm{\theta}$ marginal $ \vartheta_{0}\left(\bm{\theta}(0)\right)$ is a product von Mises PDF\footnote{the factor $2$ inside the cosine ensures the range $[0,2\pi)$; it can be dispensed if we instead use the range $[-\pi,\pi)$ for the angular variables, as common in the directional statistics literature \cite{mardia2009directional}.} \cite{mardia2008multivariate,mardia2014some} supported over $\mathbb{T}^{5}$ with mean angles (in rad)
\begin{align}
\left(\mu_{\theta_{1}}(0),\hdots,\mu_{\theta_{5}}(0)\right)=\left(0, 6.1963, 6.0612, 6.0350, 6.0500\right),
\label{MeanAngleInitialIEEE14}	
\end{align}
and concentration parameter $\kappa_{i}\geq 0$ set as 
\[(\kappa_{1},\hdots,\kappa_5) = \left(5,6,7,4,5\right).\]
In \eqref{rho0IEEE14}, $I_{0}(\cdot)$ denotes the modified Bessel function of the first kind with order zero, given by $I_{0}(\kappa) = \sum_{r=0}^{\infty} \frac{\left(\kappa^{2}/4\right)^{r}}{(r!)^{2}}$, and can be evaluated via MATLAB command \texttt{besseli(0,$\cdot$)}.
